Universidade Federal de Santa Catarina - UFSC

### 2017-04-26 monograph/proposal/methods.tex
Fixed the `\RaggedRight` usage on monograph/proposal/methods.tex by
https://tex.stackexchange.com/questions/366803/how-to-fix-url-overfull-underfull-on-emumeration
Fixed space between list items being disabled by `parskip` package.
Properly formated the monograph/proposal/methods.tex lists.

    \begin{sloppypar}
    \medskip
    \begin{myquote}
    \begin{enumerate}[nolistsep,leftmargin=*]

@@

\begin{comment}

@@

    Estudei/busquei ao longo do que há de publicações científicas sobre o assunto e entrei alguns trabalhos
    na área específica e similar aos trabalhos feitos pelor formatadores de códigos (Beautifiers). Nessa
    modalidade de trabalho, pode-se confundir-se com artigos que tratam sobre o `Prettyprint`, que trata-se
    de colorir o texto e exibir-lo ao usuário. O que não é o que se busca nesse trabalho, mas sim fazer
    alterações no texto sobre a forma como ele é estruturado, apresentado ao usuário e salvo em disco.
    Seguem as seguintes publicações:

    \url{https://www.researchgate.net/publication/228540036_An_industrial_application_of_context-sensitive_formatting}

    \url{http://www.suodenjoki.dk/us/archive/2010/cpp-checkstyle.htm}

    \url{http://www.basicinputoutput.com/2014/08/uncrustify-your-bios.html}

    \url{http://prettyprinter.de/}
    \url{http://www.softpanorama.org/Utilities/beautifiers.shtml}

    Towards a universal code formatter through machine learning:
    --
    In this paper, we solve the formatter construction problem
    using a novel approach, one that automatically derives formatters
    for any given language without intervention from a
    language expert. We introduce a code formatter called CODEBUFF
    that uses machine learning to abstract formatting rules
    from a representative corpus, using a carefully designed feature
    set. Our experiments on Java, SQL, and ANTLR grammars
    show that CODEBUFF is efficient, has excellent accuracy,
    and is grammar invariant for a given language. It also generalizes
    to a 4th language tested during manuscript preparation.
    -->
    \url{http://dl.acm.org/citation.cfm?id=2997383}
    \url{http://homepages.cwi.nl/~jurgenv/papers/SLE16.pdf}

    \url{https://www.google.com/search?q=universal+source+code+formatter}
    \url{https://www.google.com/search?q=universal+source+code+beautifier}

    \url{http://en.wikipedia.org/wiki/Indent_style}
    \url{https://en.wikipedia.org/wiki/Programming_style}
    \url{https://en.wikipedia.org/wiki/Scope_(computer_science)}

    \url{http://wiki.c2.com/?CodingStyle}
    \url{https://github.com/google/code-prettify}
    \url{https://github.com/uncrustify/uncrustify}

    \url{https://en.wikipedia.org/wiki/Prettyprint}
    \url{https://www.researchgate.net/search.Search.html?query=formatting%20source%20code&type=publication}
    \url{https://www.researchgate.net/search.Search.html?query=pretty%20print%20source%20code&type=publication}

    \url{https://github.com/gchpaco/gopprint}
    \url{http://dl.acm.org.sci-hub.io/citation.cfm?id=357115}
    \url{https://www.cs.indiana.edu/~sabry/papers/yield-pp.pdf}

    \url{http://www.worldcat.org/title/beautiful-code-a-customizable-code-beautifier-for-java/oclc/56564674}
    \url{https://www.researchgate.net/publication/34736049_Beautiful_code_a_customizable_code_beautifier_for_Java}
    \url{https://vufind.carli.illinois.edu/vf-ncc/Record/ncc_118189/Holdings}

    \url{https://www.researchgate.net/publication/4283921_Smart_Formatter_Learning_Coding_Style_from_Existing_Source_Code}
    \url{http://www.ing.unisannio.it/mdipenta/index.html}
    \url{https://github.com/iain/rspec-smart-formatter}

    \url{https://www.researchgate.net/publication/2543984_Source_Code_Files_as_Structured_Documents}
    \url{https://en.wikipedia.org/wiki/SrcML}

    \url{https://www.researchgate.net/publication/228540036_An_industrial_application_of_context-sensitive_formatting}
    \url{https://www.researchgate.net/publication/234809222_Program_indentation_and_comprehensibility}

@@

    \url{https://en.wikipedia.org/wiki/Obfuscation_(software)}

    \url{http://www.semdesigns.com/Products/Obfuscators/index.html}

\end{comment}

>>>>

    \medskip
    \begin{sloppypar}
    \begin{myquote}\RaggedRight
    \begin{enumerate}[leftmargin=*,parsep=0pt]

@@

@@

    Após a busca do que há de publicações científicas sobre o assunto e entra-se alguns trabalhos na
    área específica e similar aos trabalhos feitos pelor formatadores de códigos (Beautifiers).
    Nessa modalidade de trabalho, pode-se confundir-se com artigos que tratam sobre o `Prettyprint`,
    que trata-se de colorir o texto e exibir-lo ao usuário. O que não é o que se busca nesse
    trabalho, mas sim fazer alterações no texto sobre a forma como ele é estruturado, apresentado ao
    usuário e salvo em disco. Seguem as seguintes publicações:

    % How to add `parsep` to `itemsep` and set `parsep` to 0pt, when declaring my list?
    % https://tex.stackexchange.com/questions/366904/how-to-add-parsep-to-itemsep-and-set-parsep-to-0pt-when-declaring-my-list
    \begin{sloppypar}
    \begin{myquote}\RaggedRight
    \begin{enumerate}[leftmargin=*,parsep=0pt]

    \item \url{https://www.researchgate.net/publication/228540036_An_industrial_application_of_context-sensitive_formatting}

    \item \url{http://www.suodenjoki.dk/us/archive/2010/cpp-checkstyle.htm}

    \item \url{http://www.basicinputoutput.com/2014/08/uncrustify-your-bios.html}

    \item \url{http://prettyprinter.de/}

    \item \url{http://www.softpanorama.org/Utilities/beautifiers.shtml}

    Towards a universal code formatter through machine learning:

    In this paper, we solve the formatter construction problem using a novel approach, one that
    automatically derives formatters for any given language without intervention from a language
    expert. We introduce a code formatter called CODEBUFF that uses machine learning to abstract
    formatting rules from a representative corpus, using a carefully designed feature set. Our
    experiments on Java, SQL, and ANTLR grammars show that CODEBUFF is efficient, has excellent
    accuracy, and is grammar invariant for a given language. It also generalizes to a 4th language
    tested during manuscript preparation.

    \item \url{http://dl.acm.org/citation.cfm?id=2997383}
    \begin{enumerate}[nolistsep,topsep=0pt,label=$\star$]
        \item \url{http://homepages.cwi.nl/~jurgenv/papers/SLE16.pdf}
    \end{enumerate}

    \item \url{https://www.google.com/search?q=universal+source+code+formatter}
    \begin{enumerate}[nolistsep,topsep=0pt,label=$\star$]
        \item \url{https://www.google.com/search?q=universal+source+code+beautifier}
    \end{enumerate}

    \item \url{http://en.wikipedia.org/wiki/Indent_style}
    \begin{enumerate}[nolistsep,topsep=0pt,label=$\star$]
        \item \url{https://en.wikipedia.org/wiki/Programming_style}
        \item \url{https://en.wikipedia.org/wiki/Scope_(computer_science)}
    \end{enumerate}

    \item \url{http://wiki.c2.com/?CodingStyle}
    \begin{enumerate}[nolistsep,topsep=0pt,label=$\star$]
        \item \url{https://github.com/google/code-prettify}
        \item \url{https://github.com/uncrustify/uncrustify}
    \end{enumerate}

    \item \url{https://en.wikipedia.org/wiki/Prettyprint}
    \begin{enumerate}[nolistsep,topsep=0pt,label=$\star$]
        \item \url{https://www.researchgate.net/search.Search.html?query=formatting%20source%20code&type=publication}
        \item \url{https://www.researchgate.net/search.Search.html?query=pretty%20print%20source%20code&type=publication}
    \end{enumerate}

    \item \url{https://github.com/gchpaco/gopprint}
    \begin{enumerate}[nolistsep,topsep=0pt,label=$\star$]
        \item \url{http://dl.acm.org.sci-hub.io/citation.cfm?id=357115}
        \item \url{https://www.cs.indiana.edu/~sabry/papers/yield-pp.pdf}
    \end{enumerate}

    \item \url{http://www.worldcat.org/title/beautiful-code-a-customizable-code-beautifier-for-java/oclc/56564674}
    \begin{enumerate}[nolistsep,topsep=0pt,label=$\star$]
        \item \url{https://www.researchgate.net/publication/34736049_Beautiful_code_a_customizable_code_beautifier_for_Java}
        \item \url{https://vufind.carli.illinois.edu/vf-ncc/Record/ncc_118189/Holdings}
    \end{enumerate}

    \item \url{https://www.researchgate.net/publication/4283921_Smart_Formatter_Learning_Coding_Style_from_Existing_Source_Code}
    \begin{enumerate}[nolistsep,topsep=0pt,label=$\star$]
        \item \url{http://www.ing.unisannio.it/mdipenta/index.html}
        \item \url{https://github.com/iain/rspec-smart-formatter}
    \end{enumerate}

    \item \url{https://www.researchgate.net/publication/2543984_Source_Code_Files_as_Structured_Documents}
    \begin{enumerate}[nolistsep,topsep=0pt,label=$\star$]
        \item \url{https://en.wikipedia.org/wiki/SrcML}
    \end{enumerate}

    \item \url{https://www.researchgate.net/publication/228540036_An_industrial_application_of_context-sensitive_formatting}
    \begin{enumerate}[nolistsep,topsep=0pt,label=$\star$]
        \item \url{https://www.researchgate.net/publication/234809222_Program_indentation_and_comprehensibility}
    \end{enumerate}

@@

    \begin{sloppypar}
    \begin{myquote}\RaggedRight
    \begin{enumerate}[leftmargin=*,parsep=0pt]

    \item \url{https://en.wikipedia.org/wiki/Obfuscation_(software)}

    \item \url{http://www.semdesigns.com/Products/Obfuscators/index.html}
